---
title: "Shopalyst_problem_b"
Name: "Sai aditya garlapati"
ID: "18125760054"
output: html_document
---

```{r setup, include=FALSE}
library(readxl)
library(data.table)
library(dplyr)
library(ggplot2)
library(reshape2)
library(plotly)
library(tidyr)
library(gridExtra)
library(caret)
library(forecast)
library(kableExtra)

adcamp = read.csv('C:/Users/Aditya/Documents/Hackathons/Shopalyst/Task2/Campaign data.csv')

knitr::opts_chunk$set(echo = TRUE)
```

## Name : Sai aditya 
## id :18125760054

```{r}
filter_top10_campaigns = adcamp %>% 
  filter(Campaign.id %in% c(3001, 13003, 8801, 12502, 11801, 12501, 13001, 12505, 13002, 12503)) %>%
  group_by(Campaign.id,Date) %>%
  arrange(Campaign.id,Date)

kable(filter_top10_campaigns%>%head(10))

```
## forecasting Using RNN 

- All the popular top 10 campaigns febraury forecast has been done 
13003, 8801, 12502, 11801, 12501, 13001, 12505, 13002, 12503
- forecast for each campaign is done for the next 30 days
- campaign 1 - id is 3001
- campaign 2 - id is 13003
- campaign 3 - id is 12503
- campaign 4 - id is 8801
- campaign 5 - id is 12502
- campaign 6 - id is 11801
- campaign 7 - id is 12501
- campaign 8 - id is 13001
- campaign 9 - id is 12505
- campaign 10 - id is 13002



## Campaign 1 Forecast
```{r}
filter_campaign = adcamp %>% 
  filter(Campaign.id %in% c(3001)) %>%
  group_by(Campaign.id,Date) %>%
  arrange(Campaign.id,Date)

kable(filter_campaign%>%head(5))
library(caret)
library(forecast)
## Warning: package 'caret' was built under R version 3.4.4
## Loading required package: lattice
## Loading required package: ggplot2
## Warning: package 'ggplot2' was built under R version 3.4.4
fit = nnetar(filter_campaign$Click.count)

plot(forecast(fit,h=30))
```
## Campaign 2 Forecast

```{r}
filter_campaign = adcamp %>% 
  filter(Campaign.id %in% c(13003)) %>%
  group_by(Campaign.id,Date) %>%
  arrange(Campaign.id,Date)

kable(filter_campaign%>%head(5))

library(caret)
library(forecast)
## Warning: package 'caret' was built under R version 3.4.4
## Loading required package: lattice
## Loading required package: ggplot2
## Warning: package 'ggplot2' was built under R version 3.4.4
fit = nnetar(filter_campaign$Click.count)

plot(forecast(fit,h=30))
```

## Campaign 3 Forecast

```{r}
filter_campaign = adcamp %>% 
  filter(Campaign.id %in% c(12503)) %>%
  group_by(Campaign.id,Date) %>%
  arrange(Campaign.id,Date)

kable(filter_campaign%>%head(5))

library(caret)
library(forecast)
## Warning: package 'caret' was built under R version 3.4.4
## Loading required package: lattice
## Loading required package: ggplot2
## Warning: package 'ggplot2' was built under R version 3.4.4
fit = nnetar(filter_campaign$Click.count)

plot(forecast(fit,h=30))
```

## Campaign 4 Forecast
```{r}
filter_campaign = adcamp %>% 
  filter(Campaign.id %in% c( 8801)) %>%
  group_by(Campaign.id,Date) %>%
  arrange(Campaign.id,Date)

kable(filter_campaign%>%head(5))

library(caret)
library(forecast)
## Warning: package 'caret' was built under R version 3.4.4
## Loading required package: lattice
## Loading required package: ggplot2
## Warning: package 'ggplot2' was built under R version 3.4.4
fit = nnetar(filter_campaign$Click.count)

plot(forecast(fit,h=30))
```

## Campaign 5 Forecast
```{r}
filter_campaign = adcamp %>% 
  filter(Campaign.id %in% c( 12502)) %>%
  group_by(Campaign.id,Date) %>%
  arrange(Campaign.id,Date)

kable(filter_campaign%>%head(5))


library(caret)
library(forecast)
## Warning: package 'caret' was built under R version 3.4.4
## Loading required package: lattice
## Loading required package: ggplot2
## Warning: package 'ggplot2' was built under R version 3.4.4
fit = nnetar(filter_campaign$Click.count)

plot(forecast(fit,h=30))
```

## Campaign 6 Forecast
```{r}
filter_campaign = adcamp %>% 
  filter(Campaign.id %in% c(11801)) %>%
  group_by(Campaign.id,Date) %>%
  arrange(Campaign.id,Date)

kable(filter_campaign%>%head(5))


library(caret)
library(forecast)
## Warning: package 'caret' was built under R version 3.4.4
## Loading required package: lattice
## Loading required package: ggplot2
## Warning: package 'ggplot2' was built under R version 3.4.4
fit = nnetar(filter_campaign$Click.count)

plot(forecast(fit,h=30))
```

## Campaign 7 Forecast
```{r}
filter_campaign = adcamp %>% 
  filter(Campaign.id %in% c(12501)) %>%
  group_by(Campaign.id,Date) %>%
  arrange(Campaign.id,Date)

kable(filter_campaign%>%head(5))


library(caret)
library(forecast)
## Warning: package 'caret' was built under R version 3.4.4
## Loading required package: lattice
## Loading required package: ggplot2
## Warning: package 'ggplot2' was built under R version 3.4.4
fit = nnetar(filter_campaign$Click.count)

plot(forecast(fit,h=30))
```

## Campaign 8 Forecast
```{r}
filter_campaign = adcamp %>% 
  filter(Campaign.id %in% c(13001)) %>%
  group_by(Campaign.id,Date) %>%
  arrange(Campaign.id,Date)

kable(filter_campaign%>%head(5))


library(caret)
library(forecast)
## Warning: package 'caret' was built under R version 3.4.4
## Loading required package: lattice
## Loading required package: ggplot2
## Warning: package 'ggplot2' was built under R version 3.4.4
fit = nnetar(filter_campaign$Click.count)

plot(forecast(fit,h=30))
```

## Campaign 9 Forecast
```{r}
filter_campaign = adcamp %>% 
  filter(Campaign.id %in% c(12505)) %>%
  group_by(Campaign.id,Date) %>%
  arrange(Campaign.id,Date)

kable(filter_campaign%>%head(5))

library(caret)
library(forecast)
## Warning: package 'caret' was built under R version 3.4.4
## Loading required package: lattice
## Loading required package: ggplot2
## Warning: package 'ggplot2' was built under R version 3.4.4
fit = nnetar(filter_campaign$Click.count)

plot(forecast(fit,h=30))
```


## Campaign 10 Forecast
```{r}
filter_campaign = adcamp %>% 
  filter(Campaign.id %in% c(13002)) %>%
  group_by(Campaign.id,Date) %>%
  arrange(Campaign.id,Date)

kable(filter_campaign%>%head(5))

library(caret)
library(forecast)
## Warning: package 'caret' was built under R version 3.4.4
## Loading required package: lattice
## Loading required package: ggplot2
## Warning: package 'ggplot2' was built under R version 3.4.4
fit = nnetar(filter_campaign$Click.count)

plot(forecast(fit,h=30))